Development of Performance Regression Analysis Tool using Distributed Tracing on Microservice-based Application\\

### 2022-06-23 paper.tex
txs auto checkin

The next phase is the periodic analysis phase. This phase will run continously and the analysis will be run periodically at intervals of 5 minutes
very. This is done to continuously detect whether there is a regression and
immediately determine the source of the regression if it occurs. There are several stages of analysis
to be carried out in this phase. The first analysis stage will compare the results
transformation of data latency of all ongoing traces periodically
with the baseline latency artifact from the loading phase. The comparison will be made within a certain period. The comparison of the two latency data will produce
Kolmogorov-Smirnov statistics. If Kolmogorov-Smirnov statistics are generated
indicates that the two samples of latency data come from two different distributions
different, then it can be an indication that there has been a regression in the data capture period
the traces.

>>>>

The next phase is the periodic analysis phase. This phase will run continuously and the analysis will be run periodically at intervals of every 5 minutes. This is carried out to continuously detect whether there is a regression and
immediately determine the source of the regression if it occurs. There are several stages of analysis
to be carried out in this phase. The first analysis stage will compare the results transformation of data latency of all ongoing traces periodically with the baseline latency artifact from the loading phase. The comparison will be made within a certain period. The comparison of the two latency data will produce Kolmogorov-Smirnov statistic. If the Kolmogorov-Smirnov statistic that is generated indicates that the two samples of latency data come from two different distributions, then it can be an indication that there has been a regression in the data capture in the periodic phases the traces.
